Can the symmetric \textit{Fermi} and eROSITA bubbles be produced by tilted jets: a proof-of-concept study

### 2022-03-31 KY-3.31.tex
update

  In order to track the evolution of CRs injected by the AGN jets and make predictions of the non-thermal radiation they produce, we adopt the CR hydrodynamic formalism and model the CRs as a second fluid \citep{Zweibel2013}. The approach is similar to previous works of \cite{Guo2012} and \cite{Yang2012}, but generalized to CRs that couple with thermal gas moving with relativistic speeds. The detailed implementations in \textsc{gamer-sr} and tests of the algorithm can be found in a forthcoming paper \citep[][in prep.]{Chen2022}. In this approach, the CRs are treated as a single species without distinctions between CR electrons and protons,\
  and the CR energy density $e_{\text{cr}}$ is evolved according to Eq. \ref{E evolution}.
  The CRs are advected with the thermal gas and can have adiabatic compression and expansion with the gas. Also, we do not simulate the spectral evolution of the CRs and assume that the CR-to-gas pressure ratio is much less than 1 so that\
  the contribution of CR pressure gradient to the momentum of the gas can be ignored\
  (we will see that the ratio is around 0.1--0.2 throughout the simulations). Note that, although our later calculations of the non-thermal spectra are based on the leptonic model, only a small fraction of the simulated CRs is required to produce the observed gamma-ray and microwave emission \citep{Yang2013}.
{\color{red} KY: Is this also true in the current simulations? That is, from the simulated CR energy densities, did you have to apply a normalization constant to match with the observed gamma-ray/microwave spectra? PH: We have reached a consensus on this matter on Slack!}
Therefore, in the simulations we have neglected the cooling of CRs because it should have a negligible impact on the overall dynamics.
  %Over and above, we neglect the cooling and heating processes of CRs,\
  %such as energy losses due to synchrotron and inverse Compton emission,\
  %and CR reacceleration in shocks/turbulences.

@@

 The fiducial run (Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
 with the initial condition specified in Section \ref{Methodology}\
 shows that the edge of the outermost bubbles is a forward shock,\
 expanding to 12.5 kpc above and below the Galactic plane,\
 with a semiminor axis about 6.8 kpc on the plane.\
 The overall extent of the outermost bubbles is comparable to\
 the two spherical objects of a radius of 6-7 kpc estimated by \citet{Predehl2020}\
 for modeling the eROSITA bubbles.\
 The temperature profile (left middle panel in Fig. \ref{fig__profile}) along the positive $z$-axis in\
 Fig. \ref{fig__jetI5+ismSeed3-45deg} indicates that\
 the temperature of the smooth region (purple band in Fig. \ref{fig__profile})\ %emitting X-ray\
 is around 0.3-0.5 keV, similar to 0.3 keV observed by \citet{Miller2016} and \citet{Kataoka2018}. {\color{red} (KY: What did these observations constrain exactly?
PH: It is 0.3 keV. I have added this number in the context. See: ``...follows from the Rankine-Hugoniot condition for the temperature increase from about 0.2 keV outside the bubbles to around 0.3 keV inside$^{7,19}$" in \citealt{Predehl2020})}

@@

 An interesting feature found in our simulations is that there are a pair of innermost bubbles\
 (dashed box in the top panel of Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
 extending out from the GC on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$--$10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma.\
 The close-up view (right column in Fig. \ref{fig__profile}) of the vertical profiles\
 and slices (Fig. \ref{fig__innerbubbles})\
 demonstrate that there is a sharp pressure jump at the edge of the innermost bubbles at $z=3.62$ kpc,\
 indicating that the innermost bubbles are an expanding reverse shock.\ {\color{red} KY: Is it verified that the reverse shock is expanding outward? PH: Yes. I have checked that with multiple slices in different time. The reverse shock is expanding outward.}
 The high-density upstream of the reverse shock requires\
 an even higher density downstream.\
 Continuing outward, there exists a dense shell before the gas density drops to values further downstream.
 %Continuing outward, the higher density must match with low density further downstream;\
 %thus there exists a dense shell.\
 The turbulent plasma is therefore bracketed between the downstream of reverse shock\
 and of the outermost forward shock, thus heating the turbulent plasma up considerably.

@@

 \begin{figure}%
      \captionsetup[subfigure]{labelformat=simple}
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-a}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-a}%
      \end{subfigure}%
      \hspace{10pt}%
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-b}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-b}%
      \end{subfigure}%
      \hspace{-2pt}%
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-c}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-c}%
      \end{subfigure}%
      \hspace{-2pt}%
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-d}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-d}%
     \end{subfigure}%
      \caption{
             The slices of pressure (top), temperature (middle), and number density (bottom)\
             at the end of simulation $t=12.39$ Myr.\
             The slices pass through a bipolar jet source injecting along $z=-y$ direction\
             for a duration $t=0$--$1.2$ Myr.\
             Comparison between the clumpy (Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
             and the smooth disks (Fig. \ref{fig__jetI5+ismSeed3-45deg-b}) in a stratified atmosphere\
             shows that the initial density distribution of the dense disk has an insignificant effect\
             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disk\
             in an uniform atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-c}) is nearly spherical,\
             suggesting that the stratification facilitates the elongation of the outermost bubbles significantly.\
             Fig. \ref{fig__jetI5+ismSeed3-45deg-c} and \ref{fig__jetI5+ismSeed3-45deg-d}\
             reveal that the development of the innermost bubbles\
             is always associated with the disk. Also, without the disk (Fig. \ref{fig__jetI5+ismSeed3-45deg-d}),\
             the outermost bubbles and the turbulent plasma would be oblique,
             indicating that the dense disk is crucial for the production of symmetric Galactic bubbles.\ {\color{red} KY: Consider reducing the caption as it is essentially the same as the text. PH: Thanks! I would say figures and captions must be self-explanatory i.e. always summarize the key conclusions of this figure instead of just describing how this figure is plotted. This is the reason why the caption is a little long... \textasciicircum\textasciicircum"}
      }
      \label{fig__jetI5+ismSeed3-45deg}
 \end{figure}%

@@

  {\color{red} KY: Please rewrite the following two paragraphs so that (1) the overall agreement between the simulated and observed bubble morphology and profiles are emphasized before discussing about discrepancies, and (2) some of the disagreement for the northern bubble could be due to the North Polar Spur. PH: done!}

@@

Therefore, the CRe generating the gamma-ray emission would need to be re-accelerated
by in-situ acceleration mechanisms such as shocks or turbulence.
Since the forward shock is rather far away from the gamma-ray bubbles,
re-acceleration is more likely associated with turbulence \citep{Mertsch2011,Mertsch2019},
possibly in balance with the IC and synchrotron cooling. We will investigate the competition between stochastic acceleration and radiative cooling
in a future work.

Overall, our results imply that, whatever the true re-acceleration and cooling mechanisms are,
the CRe spectrum at the present time has to be spatially uniform with
a spectral index of 2.4 in order to fit the observed spectra.

@@

%\item The randomness of the clumpy disk has an insignificant impact on the overall dynamic of the Galactic bubbles.\
%      The development of the reverse shocks (the innermost bubbles) is always associated with the dense disk,\
%      without the disc, the outermost bubbles and the turbulent plasma will be oblique,\
%      indicating the dense disc is crucial for\
%      the symmetry of the Galactic bubbles and for the innermost bubbles formation.
      {\color{red} KY: I removed the second point about the innermost bubbles for now, because I think the following two points should be separated: (1) inclusion of the disk is critical for forming symmetric Galactic bubbles, (2) we found a pair of innermost bubbles which are reverse shocks (and perhaps comment on their properties and/or observable signatures). PH: done! }
\item The development of the expanding forward-reverse shock pair is always associated with the dense disk. Also, without the thin disk, only forward shocks exist. The forward-reverse shock pair heats the turbulent plasma up considerably ($\sim2$ keV) as the plasma is bracketed between their downstream. There exists a dense shell that fits closely to the reverse shock because the gas is immediately compressed as it passes outward through the reverse shock while coinciding with the low gas density further downstream.

\item In the oblique jet scenario, the edge of the eROSITA bubbles is a forward shock,\
      originally driven by oblique bipolar jets emanating from the GC 12.39 Myr ago for a duration of 1.2 Myr\
      and significantly expanded within the stratified atmosphere afterwards.\
      The overall extent of the simulated X-ray bubbles is comparable to that of the eROSITA bubbles, though not as limb-brightened.\
      Future models including shock-accelerated CRs may help to resolve this issue by increasing the compressibility of the fluid and enhancing the thermal Bremsstrahlung emissivity at the edge of the X-ray bubbles.
      %The simulated eROSITA bubbles are not as limb-brightened as the observation.\
      %A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
      %in which CRs could increase the compressibility of the fluid,\
      %resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
\item Followed by the forward shock is a turbulent, hot plasma ($\sim2$ keV) filled with the injected CRs in pressure balance with the shocked medium, which we interpret as the \textit{Fermi} bubbles.\
      The similarity of the morphology, temperature, and gamma-ray spectrum between\
      simulated and observed bubbles suggests that\
      the edge of the \textit{Fermi} bubbles are likely associated with the contact discontinuity between the turbulent, hot plasma and the post-shock medium. The surface of the simulated bubbles is not as smooth as the observed ones; inclusion of magnetic fields in the future may help suppress the instabilities at the bubble surface due to the mangetic draping effect.
\item Assuming a leptonic model with a spatially uniform, power-law CRe spectrum ranging from 0.5 MeV to 562.1 GeV, we showed that the observed gamma-ray and microwave spectra can simultaneously reproduced. The best-fit\
      CRe power-law index is found to be 2.4.
\item The elapsed time of 12.39 Myr required for the simulated bubbles
      to reach the desired morphology
      is ten times longer than the typical synchrotron and IC cooling time scale of
      high energy ($\sim100$ GeV) CRe. Thus, re-acceleration of CRe must be considered
      in this model. As opposed to shock acceleration,
      the acceleration of CRe that can compete with IC and synchrotron cooling
      may be dominated by the stochastic acceleration associated with the Galactic magnetic field,
      since the forward shock is rather far away from the gamma-ray bubbles.
      We will investigate the competition between stochastic acceleration and radiative cooling
      in a future work.
      {\color{red} KY: This item is to be modified according to the newly added text in the Discussion section. PH: done!}
\end{itemize}

@@

We observe that higher density (F$\rightarrow$C$\rightarrow$E) of the source\
can enhance the intensity of the shocks driven into the atmosphere,\
and makes the post-shock region hotter,\
as well as leads the bubbles to be more asymmetric about the GC.
This is because the denser jets are more likely to\
break through the thin disk in a short time\
and more difficult to be elongated by stratified atmosphere afterward.

On the other hand, when we increase the magnitude of velocity\
(G$\rightarrow$C$\rightarrow$A) such that\
the corresponding kinetic energies are the same as when increasing\
density, the bubble morphology of two will be similar.\
This demonstrates that the morphology/dynamic of bubbles is mainly determined by\
kinetic energy of a jet flow.

Finally, when we increase the thermal energy (B$\rightarrow$C$\rightarrow$D)\
of the jet source such that the thermal energy increase by\
the same amount as the kinetic energy,\
we find that the morphology of bubbles is basically unchanged,\
but the evolution of bubbles can be slightly accelerated.

>>>>

  In order to track the evolution of CRs injected by the AGN jets and make predictions of the non-thermal radiation they produce, we adopt the CR hydrodynamic formalism and model the CRs as a second fluid \citep{Zweibel2013}. The approach is similar to previous works of \cite{Guo2012} and \cite{Yang2012}, but generalized to CRs that couple with thermal gas moving with relativistic speeds. The detailed implementations in \textsc{gamer-sr} and tests of the algorithm can be found in a forthcoming paper \citep[][in prep.]{Chen2022}. In this approach, the CRs are treated as a single species without distinctions between CR electrons and protons,\
  and the CR energy density $e_{\text{cr}}$ is evolved according to Eq. \ref{E evolution}.
  The CRs are advected with the thermal gas and can have adiabatic compression and expansion with the gas. Also, we do not simulate the spectral evolution of the CRs and assume that the CR-to-gas pressure ratio is much less than 1 so that\
  the contribution of CR pressure gradient to the momentum of the gas can be ignored\
  (we will see that the ratio is around 0.1--0.2 throughout the simulations). %Note that, although our later calculations of the non-thermal spectra are based on the leptonic model, only a small fraction of the simulated CRs is required to produce the observed gamma-ray and microwave emission \citep{Yang2013}.
%{\color{red} KY: Is this also true in the current simulations? That is, from the simulated CR energy densities, did you have to apply a normalization constant to match with the observed gamma-ray/microwave spectra? PH: We have reached a consensus on this matter on Slack!}
Therefore, in the simulations we have neglected the cooling of CRs because it should have a negligible impact on the overall dynamics.
  %Over and above, we neglect the cooling and heating processes of CRs,\
  %such as energy losses due to synchrotron and inverse Compton emission,\
  %and CR reacceleration in shocks/turbulences.

@@

 The fiducial run (Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
 with the initial condition specified in Section \ref{Methodology}\
 shows that the edge of the outermost bubbles is a forward shock,\
 expanding to 12.5 kpc above and below the Galactic plane,\
 with a semiminor axis about 6.8 kpc on the plane.\
 The overall extent of the outermost bubbles is comparable to\
 the two spherical objects of a radius of 6-7 kpc estimated by \citet{Predehl2020}\
 for modeling the eROSITA bubbles.\
 The temperature profile (left middle panel in Fig. \ref{fig__profile}) along the positive $z$-axis in\
 Fig. \ref{fig__jetI5+ismSeed3-45deg} indicates that\
 the temperature of the smooth region (purple band in Fig. \ref{fig__profile})\ %emitting X-ray\
 is around 0.3-0.5 keV, similar to 0.3 keV observed by \citet{Miller2016} and \citet{Kataoka2018}. %{\color{red} (KY: What did these observations constrain exactly? PH: It is 0.3 keV. I have added this number in the context. See: ``...follows from the Rankine-Hugoniot condition for the temperature increase from about 0.2 keV outside the bubbles to around 0.3 keV inside$^{7,19}$" in \citealt{Predehl2020})}

@@

 An interesting feature found in our simulations is that there are a pair of innermost bubbles\
 (dashed box in the top panel of Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
 extending out from the GC on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$--$10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma.\
 The close-up view (right column in Fig. \ref{fig__profile}) of the vertical profiles\
 and slices (Fig. \ref{fig__innerbubbles})\
 demonstrate that there is a sharp pressure jump at the edge of the innermost bubbles at $z=3.62$ kpc,\
 indicating that the innermost bubbles are an expanding reverse shock.\ %{\color{red} KY: Is it verified that the reverse shock is expanding outward? PH: Yes. I have checked that with multiple slices in different time. The reverse shock is expanding outward.}
 The high-density upstream of the reverse shock requires\
 an even higher density downstream.\
 Continuing outward, there exists a dense shell before the gas density drops to values further downstream.
 %Continuing outward, the higher density must match with low density further downstream;\
 %thus there exists a dense shell.\
 The turbulent plasma is therefore bracketed between the downstream of reverse shock\
 and of the outermost forward shock, thus heating the turbulent plasma up considerably.

@@

 \begin{figure}%
      \captionsetup[subfigure]{labelformat=simple}
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-a}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-a}%
      \end{subfigure}%
      \hspace{10pt}%
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-b}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-b}%
      \end{subfigure}%
      \hspace{-2pt}%
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-c}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-c}%
      \end{subfigure}%
      \hspace{-2pt}%
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-d}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-d}%
     \end{subfigure}%
      \caption{
             The slices of pressure (top), temperature (middle), and number density (bottom)\
             at the end of simulation $t=12.39$ Myr.\
             The slices pass through a bipolar jet source injecting along $z=-y$ direction\
             for a duration $t=0$--$1.2$ Myr.\
             Comparison between the clumpy (Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
             and the smooth disks (Fig. \ref{fig__jetI5+ismSeed3-45deg-b}) in a stratified atmosphere\
             shows that the initial density distribution of the dense disk has an insignificant effect\
             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disk\
             in an uniform atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-c}) is nearly spherical,\
             suggesting that the stratification facilitates the elongation of the outermost bubbles significantly.\
             Fig. \ref{fig__jetI5+ismSeed3-45deg-c} and \ref{fig__jetI5+ismSeed3-45deg-d}\
             reveal that the development of the innermost bubbles\
             is always associated with the disk. Also, without the disk (Fig. \ref{fig__jetI5+ismSeed3-45deg-d}),\
             the outermost bubbles and the turbulent plasma would be oblique,
             indicating that the dense disk is crucial for the production of symmetric Galactic bubbles.\ %{\color{red} KY: Consider reducing the caption as it is essentially the same as the text. PH: Thanks! I would say figures and captions must be self-explanatory i.e. always summarize the key conclusions of this figure instead of just describing how this figure is plotted. This is the reason why the caption is a little long... \textasciicircum\textasciicircum"}
      }
      \label{fig__jetI5+ismSeed3-45deg}
 \end{figure}%

@@

%  {\color{red} KY: Please rewrite the following two paragraphs so that (1) the overall agreement between the simulated and observed bubble morphology and profiles are emphasized before discussing about discrepancies, and (2) some of the disagreement for the northern bubble could be due to the North Polar Spur. PH: done!}

@@

Therefore, the CRe generating the gamma-ray emission would need to be re-accelerated
by in-situ acceleration mechanisms such as shocks or turbulence.
Since the forward shock is rather far away from the gamma-ray bubbles,
re-acceleration is more likely associated with turbulence \citep{Mertsch2011,Mertsch2019},
possibly in balance with the IC and synchrotron cooling. We will investigate the competition between stochastic acceleration and radiative cooling
in future work.

Overall, our results imply that in the oblique-jet scenario, whatever the true re-acceleration and cooling mechanisms are,
the CRe spectrum at the present time has to be spatially uniform with
a spectral index of 2.4 in order to fit the observed spectra.

@@

%\item The randomness of the clumpy disk has an insignificant impact on the overall dynamic of the Galactic bubbles.\
%      The development of the reverse shocks (the innermost bubbles) is always associated with the dense disk,\
%      without the disc, the outermost bubbles and the turbulent plasma will be oblique,\
%      indicating the dense disc is crucial for\
%      the symmetry of the Galactic bubbles and for the innermost bubbles formation.
%      {\color{red} KY: I removed the second point about the innermost bubbles for now, because I think the following two points should be separated: (1) inclusion of the disk is critical for forming symmetric Galactic bubbles, (2) we found a pair of innermost bubbles which are reverse shocks (and perhaps comment on their properties and/or observable signatures). PH: done! }
\item The development of the expanding forward-reverse shock pair is always associated with the dense disk. Also, without the thin disk, only forward shocks exist. The forward-reverse shock pair heats the turbulent plasma up considerably ($\sim2$ keV) as the plasma is bracketed between their downstream. There exists a dense shell that fits closely to the reverse shock because the gas is immediately compressed as it passes outward through the reverse shock while coinciding with the low gas density further downstream.

\item In the oblique jet scenario, the edge of the eROSITA bubbles is a forward shock,\
      originally driven by oblique bipolar jets emanating from the GC 12.39 Myr ago for a duration of 1.2 Myr\
      and significantly expanded within the stratified atmosphere afterwards.\
      The overall extent of the simulated X-ray bubbles is comparable to that of the eROSITA bubbles, though not as limb-brightened.\
      Future models including shock-accelerated CRs may help to resolve this issue by increasing the compressibility of the fluid and enhancing the thermal Bremsstrahlung emissivity at the edge of the X-ray bubbles.
      %The simulated eROSITA bubbles are not as limb-brightened as the observation.\
      %A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
      %in which CRs could increase the compressibility of the fluid,\
      %resulting in the enhanced thermal Bremsstrahlung emissivity that is proportional to density squared.
\item Followed by the forward shock is a turbulent, hot plasma ($\sim2$ keV) filled with the injected CRs in pressure balance with the shocked medium, which we interpret as the \textit{Fermi} bubbles.\
      The similarity of the morphology, temperature, and gamma-ray spectrum between\
      simulated and observed bubbles suggests that\
      the edge of the \textit{Fermi} bubbles are likely associated with the contact discontinuity between the turbulent, hot plasma and the post-shock medium. The surface of the simulated bubbles is not as smooth as the observed ones; inclusion of magnetic fields in the future may help suppress the instabilities at the bubble surface due to the mangetic draping effect.
\item Assuming a leptonic model with a spatially uniform, power-law CRe spectrum ranging from 0.5 MeV to 562.1 GeV, we showed that the observed gamma-ray and microwave spectra can simultaneously reproduced. The best-fit\
      CRe power-law index is found to be 2.4.
\item The elapsed time of 12.39 Myr required for the simulated bubbles
      to reach the desired morphology
      is ten times longer than the typical synchrotron and IC cooling time scale of
      high energy ($\sim100$ GeV) CRe. Thus, re-acceleration of CRe by shocks or turbulence must be considered
      in this model. Since the forward shock is rather far away from the gamma-ray bubbles, stochastic acceleration of CRs by turbulence appears to be more plausible.\
      We will investigate the competition between stochastic acceleration and radiative cooling
      in a future work.
      %{\color{red} KY: This item is to be modified according to the newly added text in the Discussion section. PH: done!}
\end{itemize}

@@

We observe that higher density (F$\rightarrow$C$\rightarrow$E) of the source\
can enhance the intensity of the shocks driven into the atmosphere,\
and makes the post-shock region hotter,\
as well as leads the bubbles to be more asymmetric about the GC.
This is because the denser jets are more likely to\
break through the thin disk in a short time\
and {\color{red} KY: or doesn't have enough time to interact with disk to change its orientations?} more difficult to be elongated by stratified atmosphere afterward.

On the other hand, when we increase the magnitude of velocity\
(G$\rightarrow$C$\rightarrow$A) such that\
the corresponding kinetic energies are the same as when increasing\
density, the bubble morphology of two will be similar.{\color{red} KY: The meaning of this sentence is a bit unclear. You mean changing the source density and changing the velocity will give similar results, right?}\
This demonstrates that the morphology/dynamic of bubbles is mainly determined by\
kinetic energy of a jet flow.

Finally, when we increase the thermal energy (B$\rightarrow$C$\rightarrow$D)\
of the jet source such that the thermal energy increase by\
the same amount as the kinetic energy,\
we find that the morphology of bubbles is basically unchanged,\
but the evolution of bubbles can be slightly accelerated.{\color{red} KY: Is it true that Run B and C look essentially identical even if their jet thermal density is quite different?}
